---
title: "Night-time Light in Guangdong"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r cars}
library(sf)
library(raster)
library(tidyverse)
library(readxl)
library(ggplot2)
library(rgdal)
library(dplyr)
library(tmap)
library(tmaptools)
library(sp)
library(gridExtra)
library(ggthemes)
library(plyr)
library(geojsonio)
library(plotly)
library(broom)
library(mapview)
library(crosstalk)
library(spdep)
library(car)
library(fs)
library(janitor)
```


Input the gpkg file(pre-proccessed in QGIS):[gd.gpkg] (https://github.com/akiakutaji/Economic-spatial-pattern-in-Guangdong/blob/main/Desprictive%20statisics%20and%20Regression(Rmd)/gd.gpkg)


```{r}
st_layers("gd.gpkg")

gd_city<-st_read("gd.gpkg",layer='gd_city_attribute') 
gd_county<- st_read("gd.gpkg",layer='gd_county_attribute')     

plot(gd_city)
```
```{r}
plot(gd_county)
```


### Check the distribution of each variable
F1: Per Capita Gross Domestic Product Data
F2: Number of Enterprises (Unit) Data
F3: Total Profit (10000 yuan) Data
F4: Invest in Fixed Assets Data
F5: Employed Persons Data

#### City scale
```{r}
par(mfrow = c(2,3))
hist(gd_city$F1, breaks=30,main="Histogram of F1",col="lightblue",xlab=NULL,ylab=NULL)
hist(gd_city$F2, breaks=30,main="Histogram of F2",col="lightblue",xlab=NULL,ylab=NULL)
hist(gd_city$F3, breaks=30,main="Histogram of F3",col="lightblue",xlab=NULL,ylab=NULL)
hist(gd_city$F4, breaks=30,main="Histogram of F4",col="lightblue",xlab=NULL,ylab=NULL)
hist(gd_city$F5, breaks=30,main="Histogram of F5",col="lightblue",xlab=NULL,ylab=NULL)
hist(gd_city$night_light_mean, breaks=30,main="Histogram of VIIRS",col="lightblue",xlab=NULL,ylab=NULL)
```
#### County scale
```{r}
par(mfrow = c(2,3))
hist(gd_county$F1, breaks=30,col="lightblue",main="Histogram of F1",xlab=NULL,ylab=NULL)
hist(gd_county$F2, breaks=30,main="Histogram of F2",col="lightblue",xlab=NULL,ylab=NULL)
hist(gd_county$F3, breaks=30,main="Histogram of F3",col="lightblue",xlab=NULL,ylab=NULL)
hist(gd_county$F4, breaks=30,main="Histogram of F4",col="lightblue",xlab=NULL,ylab=NULL)
hist(gd_county$F5, breaks=30,main="Histogram of F5",col="lightblue",xlab=NULL,ylab=NULL)
hist(gd_county$night_light_mean, breaks=30,main="Histogram of VIIRS",col="lightblue",xlab=NULL,ylab=NULL)

```
### Get the log of variables and cheack their distribution again

#### City scale

```{r}
city_log<-st_read("gd.gpkg",layer='gd_city_log') 
county_log<- st_read("gd.gpkg",layer='gd_county_log')
```


```{r}
par(mfrow = c(2,3))
#hist(city_log$lnf1, breaks=30,  col="light")
#lines(density(city_log$lnf1))
#hist(city_log$lnf2, breaks=30,  col="red")
#hist(city_log$lnf3, breaks=30,  col="red")
#hist(city_log$lnf4, breaks=30,  col="red")
#hist(city_log$lnf5, breaks=30,  col="red")
#hist(city_log$lnnight, breaks=30,  col="red")

h_city_1 <- hist(city_log$lnf1,breaks = 20,col="lightblue",xlab = NULL,main = "Histogram of logF1")
x_city_1 <- city_log$lnf1
xfit_city_1 <- seq(min(x_city_1),max(x_city_1),length=40)
yfit_city_1 <- dnorm(xfit_city_1,mean = mean(x_city_1),sd = sd(x_city_1))
yfit_city_1 <- yfit_city_1*diff(h_city_1$mids[1:2])*length(x_city_1)
lines(xfit_city_1,yfit_city_1,col="black",lwd=2)
box()

h_city_2 <- hist(city_log$lnf2,breaks = 20,col="lightblue",xlab = NULL,main = "Histogram of logF2")
x_city_2 <- city_log$lnf2
xfit_city_2 <- seq(min(x_city_2),max(x_city_2),length=40)
yfit_city_2 <- dnorm(xfit_city_2,mean = mean(x_city_2),sd = sd(x_city_2))
yfit_city_2 <- yfit_city_2*diff(h_city_2$mids[1:2])*length(x_city_2)
lines(xfit_city_2,yfit_city_2,col="black",lwd=2)
box()

h_city_3 <- hist(city_log$lnf3,breaks = 20,col="lightblue",xlab = NULL,main = "Histogram of logF3")
x_city_3 <- city_log$lnf3
xfit_city_3 <- seq(min(x_city_3),max(x_city_3),length=40)
yfit_city_3 <- dnorm(xfit_city_3,mean = mean(x_city_3),sd = sd(x_city_3))
yfit_city_3 <- yfit_city_3*diff(h_city_3$mids[1:2])*length(x_city_3)
lines(xfit_city_3,yfit_city_3,col="black",lwd=2)
box()

h_city_4 <- hist(city_log$lnf4,breaks = 20,col="lightblue",xlab = NULL,main = "Histogram of logF4")
x_city_4 <- city_log$lnf4
xfit_city_4 <- seq(min(x_city_4),max(x_city_4),length=40)
yfit_city_4 <- dnorm(xfit_city_4,mean = mean(x_city_4),sd = sd(x_city_4))
yfit_city_4 <- yfit_city_4*diff(h_city_4$mids[1:2])*length(x_city_4)
lines(xfit_city_4,yfit_city_4,col="black",lwd=2)
box()

h_city_5 <- hist(city_log$lnf5,breaks = 20,col="lightblue",xlab = NULL,main = "Histogram of logF5")
x_city_5 <- city_log$lnf5
xfit_city_5 <- seq(min(x_city_5),max(x_city_5),length=40)
yfit_city_5 <- dnorm(xfit_city_5,mean = mean(x_city_5),sd = sd(x_city_5))
yfit_city_5 <- yfit_city_5*diff(h_city_5$mids[1:2])*length(x_city_5)
lines(xfit_city_5,yfit_city_5,col="black",lwd=2)
box()

h_city_6 <- hist(city_log$lnnight,breaks = 20,col="lightblue",xlab = NULL,main = "Histogram of lognight")
x_city_6 <- city_log$lnnight
xfit_city_6 <- seq(min(x_city_6),max(x_city_6),length=40)
yfit_city_6 <- dnorm(xfit_city_6,mean = mean(x_city_6),sd = sd(x_city_6))
yfit_city_6 <- yfit_city_6*diff(h_city_6$mids[1:2])*length(x_city_6)
lines(xfit_city_6,yfit_city_6,col="black",lwd=2)
box()

```
#### gd_county
```{r}
par(mfrow = c(2,3))
#hist(county_log$lnf1, breaks=30,  col="red")
#hist(county_log$lnf2, breaks=30,  col="red")
#hist(county_log$lnf3, breaks=30,  col="red")
#hist(county_log$lnf4, breaks=30,  col="red")
#hist(county_log$lnf5, breaks=30,  col="red")
#hist(county_log$lnnight, breaks=30,  col="red")

h_county_1 <- hist(county_log$lnf1,breaks = 30,col="lightblue",xlab = NULL,main = "Histogram of logF1")
x_county_1 <- county_log$lnf1
xfit_county_1 <- seq(min(x_county_1),max(x_county_1),length=40)
yfit_county_1 <- dnorm(xfit_county_1,mean = mean(x_county_1),sd = sd(x_county_1))
yfit_county_1 <- yfit_county_1*diff(h_county_1$mids[1:2])*length(x_county_1)
lines(xfit_county_1,yfit_county_1,col="black",lwd=2)
box()

h_county_2 <- hist(county_log$lnf2,breaks = 30,col="lightblue",xlab = NULL,main = "Histogram of logF2")
x_county_2 <- county_log$lnf2
xfit_county_2 <- seq(min(x_county_2),max(x_county_2),length=40)
yfit_county_2 <- dnorm(xfit_county_2,mean = mean(x_county_2),sd = sd(x_county_2))
yfit_county_2 <- yfit_county_2*diff(h_county_2$mids[1:2])*length(x_county_2)
lines(xfit_county_2,yfit_county_2,col="black",lwd=2)
box()

h_county_3 <- hist(county_log$lnf3,breaks = 30,col="lightblue",xlab = NULL,main = "Histogram of logF3")
x_county_3 <- county_log$lnf3
xfit_county_3 <- seq(min(x_county_3),max(x_county_3),length=40)
yfit_county_3 <- dnorm(xfit_county_3,mean = mean(x_county_3),sd = sd(x_county_3))
yfit_county_3 <- yfit_county_3*diff(h_county_3$mids[1:2])*length(x_county_3)
lines(xfit_county_3,yfit_county_3,col="black",lwd=2)
box()

h_county_4 <- hist(county_log$lnf4,breaks = 30,col="lightblue",xlab = NULL,main = "Histogram of logF4")
x_county_4 <- county_log$lnf4
xfit_county_4 <- seq(min(x_county_4),max(x_county_4),length=40)
yfit_county_4 <- dnorm(xfit_county_4,mean = mean(x_county_4),sd = sd(x_county_4))
yfit_county_4 <- yfit_county_4*diff(h_county_4$mids[1:2])*length(x_county_4)
lines(xfit_county_4,yfit_county_4,col="black",lwd=2)
box()

h_county_5 <- hist(county_log$lnf5,breaks = 30,col="lightblue",xlab = NULL,main = "Histogram of logF5")
x_county_5 <- county_log$lnf5
xfit_county_5 <- seq(min(x_county_5),max(x_county_5),length=40)
yfit_county_5 <- dnorm(xfit_county_5,mean = mean(x_county_5),sd = sd(x_county_5))
yfit_county_5 <- yfit_county_5*diff(h_county_5$mids[1:2])*length(x_county_5)
lines(xfit_county_5,yfit_county_5,col="black",lwd=2)
box()

h_county_6 <- hist(county_log$lnnight,breaks = 30,col="lightblue",xlab = NULL,main = "Histogram of lognight")
x_county_6 <- county_log$lnnight
xfit_county_6 <- seq(min(x_county_6),max(x_county_6),length=40)
yfit_county_6 <- dnorm(xfit_county_6,mean = mean(x_county_6),sd = sd(x_county_6))
yfit_county_6 <- yfit_county_6*diff(h_county_6$mids[1:2])*length(x_county_6)
lines(xfit_county_6,yfit_county_6,col="black",lwd=2)
box()



```

### Multiple regression (OLS)
#### City scale
```{r}
Regressiondata_city<- city_log  %>%  dplyr::select(lnnight, lnf1,lnf2,lnf3,lnf4,lnf5)
city_multi_model <- lm( lnnight~ lnf2 +lnf3+ lnf4 +lnf5, data = Regressiondata_city)
tidy(city_multi_model)
```

```{r}

city_log <- city_log %>%
  mutate(model_final_res = residuals(city_multi_model))

par(mfrow=c(2,2))
plot(city_multi_model)

```
```{r}
qtm(city_log, fill = "model_final_res",title="Distribution of Residuals(City)")
```
```{r}
coordsW_city <- city_log%>%
  st_centroid()%>%
  st_geometry()

knn_coounty <-coordsW_city %>%
  knearneigh(., k=4)

city_knn <- knn_coounty %>%
  knn2nb()

knn_coounty_weight <- city_knn %>%
  nb2listw(., style="C")

city_Moran <- city_log %>%
  st_drop_geometry()%>%
  dplyr::select(model_final_res)%>%
  pull()%>%
  moran.test(., knn_coounty_weight)%>%
  tidy()

city_Moran
```
#### County scale
```{r}
Regressiondata_county<- county_log  %>%  dplyr::select(lnnight, lnf1,lnf2,lnf3,lnf4,lnf5)
county_multi_model <- lm( lnnight~ lnf2 +lnf3+ lnf4 +lnf5, data = Regressiondata_county)
tidy(county_multi_model)
```

```{r}

county_log <- county_log %>%
  mutate(model_final_res = residuals(county_multi_model))

par(mfrow=c(2,2))
plot(county_multi_model)

```
```{r}
qtm(county_log, fill = "model_final_res",title="Distribution of Residuals(County)")
```
```{r}
coordsW_county <- county_log%>%
  st_centroid()%>%
  st_geometry()

knn_coounty <-coordsW_county %>%
  knearneigh(., k=4)

county_knn <- knn_coounty %>%
  knn2nb()

knn_coounty_weight <- county_knn %>%
  nb2listw(., style="C")

county_Moran <- county_log %>%
  st_drop_geometry()%>%
  dplyr::select(model_final_res)%>%
  pull()%>%
  moran.test(., knn_coounty_weight)%>%
  tidy()

county_Moran

```

### GWR
#### City Scale
```{r}
library(spgwr)

st_crs(city_log) = 27700

city_log_SP <- city_log %>%
  as(., "Spatial")

st_crs(coordsW_city) = 27700

coordsWSP_city <- coordsW_city %>%
  as(., "Spatial")

GWRbandwidth_city <- gwr.sel(lnnight ~ lnf2 + lnf3 +lnf4 +lnf5,
                  data = city_log_SP, 
                        coords=coordsWSP_city,
                        adapt=T)
gwr.model_city = gwr(lnnight ~ lnf2 + lnf3 +lnf4 +lnf5,
                  data = city_log_SP, 
                        coords=coordsWSP_city,
                adapt=GWRbandwidth_city, 
                hatmatrix=TRUE, 
                se.fit=TRUE)
gwr.model_city
```


```{r}
results_city <- as.data.frame(gwr.model_city$SDF)

#attach coefficients to original SF
city_log_2 <- city_log %>%
  mutate(coef_lnf2 = results_city$lnf2,
         coef_lnf3 = results_city$lnf3,
         coef_lnf4 = results_city$lnf4,
         coef_lnf5 = results_city$lnf5)
```


```{r}

gwr_city_2<-tm_shape(city_log_2) +tm_polygons(col = "coef_lnf2", palette="PuBu",style="jenks",palette="YlOrBr",title = "Coefficient")+tm_layout(frame=FALSE,legend.position = c("right", "bottom"),legend.text.size = 0.6,legend.title.size = 0.7)+tm_credits("(a) Number of Enterprises (Unit)", position=c(0,0.9), size=0.7)+tm_scale_bar(position=c(0.35, 0.01),text.size = 0.5) +tm_compass(type = "arrow", position=c("left", 0.6)) 

gwr_city_3<-tm_shape(city_log_2) +tm_polygons(col = "coef_lnf3", palette="PuBu",style="jenks",palette="YlOrBr",title = "Coefficient")+tm_layout(frame=FALSE,legend.position = c("right", "bottom"),legend.text.size = 0.6,legend.title.size = 0.7)+tm_credits("(b) Total Profit (10000 yuan)", position=c(0,0.9),  size=0.7)+tm_scale_bar(position=c(0.35, 0.01),text.size = 0.5) +tm_compass(type = "arrow", position=c("left", 0.6)) 

gwr_city_4<-tm_shape(city_log_2) +tm_polygons(col = "coef_lnf4", palette="PuBu",style="jenks",palette="YlOrBr",title= "Coefficient")+tm_layout(frame=FALSE,legend.position = c("right", "bottom"),legend.text.size = 0.6,legend.title.size = 0.7)+tm_credits("(c) Invest in Fixed Assets", position=c(0,0.9),  size=0.7)+tm_scale_bar(position=c(0.35, 0.01),text.size = 0.5) +tm_compass(type = "arrow", position=c("left", 0.6)) 

gwr_city_5<-tm_shape(city_log_2) +tm_polygons(col = "coef_lnf5", palette="PuBu",style="jenks",palette="YlOrBr",title = "Coefficient")+tm_layout(frame=FALSE,legend.position = c("right", "bottom"),legend.text.size = 0.6,legend.title.size = 0.7)+tm_credits("(d) Employed Persons", position=c(0,0.9),  size=0.7)+tm_scale_bar(position=c(0.35, 0.01),text.size = 0.5) +tm_compass(type = "arrow", position=c("left", 0.6)) 

t_city=tmap_arrange(gwr_city_2,gwr_city_3,gwr_city_4,gwr_city_5)

t_city

```


#### County Scale
```{r}
st_crs(county_log) = 27700

county_log_SP <- county_log %>%
  as(., "Spatial")

st_crs(coordsW_county) = 27700

coordsWSP_county <- coordsW_county %>%
  as(., "Spatial")

GWRbandwidth_county <- gwr.sel(lnnight ~ lnf2 + lnf3 +lnf4 +lnf5,
                  data = county_log_SP, 
                        coords=coordsWSP_county,
                        adapt=T)
gwr.model_county = gwr(lnnight ~ lnf2 + lnf3 +lnf4 +lnf5,
                  data = county_log_SP, 
                        coords=coordsWSP_county,
                adapt=GWRbandwidth_county, 
                hatmatrix=TRUE, 
                se.fit=TRUE)
gwr.model_county
```


```{r}
results_county <- as.data.frame(gwr.model_county$SDF)

#attach coefficients to original SF
county_log_2 <- county_log %>%
  mutate(coef_lnf2 = results_county$lnf2,
         coef_lnf3 = results_county$lnf3,
         coef_lnf4 = results_county$lnf4,
         coef_lnf5 = results_county$lnf5)


gwr_county_2<-tm_shape(county_log_2) +tm_polygons(col = "coef_lnf2", palette="PuBu",style="jenks",palette="YlOrBr",title = "Coefficient")+tm_layout(frame=FALSE,legend.position = c("right", "bottom"),legend.text.size = 0.6,legend.title.size = 0.7)+tm_credits("(a) Number of Enterprises (Unit)", position=c(0,0.9), size=0.7)+tm_scale_bar(position=c(0.35, 0.01),text.size = 0.5) +tm_compass(type = "arrow", position=c("left", 0.6)) 

gwr_county_3<-tm_shape(county_log_2) +tm_polygons(col = "coef_lnf3", palette="PuBu",style="jenks",palette="YlOrBr",title = "Coefficient")+tm_layout(frame=FALSE,legend.position = c("right", "bottom"),legend.text.size = 0.6,legend.title.size = 0.7)+tm_credits("(b) Total Profit (10000 yuan)", position=c(0,0.9),  size=0.7)+tm_scale_bar(position=c(0.35, 0.01),text.size = 0.5) +tm_compass(type = "arrow", position=c("left", 0.6)) 

gwr_county_4<-tm_shape(county_log_2) +tm_polygons(col = "coef_lnf4", palette="PuBu",style="jenks",palette="YlOrBr",title= "Coefficient")+tm_layout(frame=FALSE,legend.position = c("right", "bottom"),legend.text.size = 0.6,legend.title.size = 0.7)+tm_credits("(c) Invest in Fixed Assets", position=c(0,0.9),  size=0.7)+tm_scale_bar(position=c(0.35, 0.01),text.size = 0.5) +tm_compass(type = "arrow", position=c("left", 0.6)) 

gwr_county_5<-tm_shape(county_log_2) +tm_polygons(col = "coef_lnf5", palette="PuBu",style="jenks",palette="YlOrBr",title = "Coefficient")+tm_layout(frame=FALSE,legend.position = c("right", "bottom"),legend.text.size = 0.6,legend.title.size = 0.7)+tm_credits("(d) Employed Persons", position=c(0,0.9),  size=0.7)+tm_scale_bar(position=c(0.35, 0.01),text.size = 0.5) +tm_compass(type = "arrow", position=c("left", 0.6)) 

t_county=tmap_arrange(gwr_county_2,gwr_county_3,gwr_county_4,gwr_county_5)

t_county

```
